elasticnet

### 2022-06-19 analysis/elasticnet.Rmd
feat: use plot(..., what = "path") introduced in ameld 0.0.25

plot(bootrcv, what = "selected", cex = 0.5)
plot(bootrcv$fit$glmnet.fit, xvar = "norm")
plot(bootrcv$fit$glmnet.fit, xvar = "lambda")
plot(bootrcv$fit$glmnet.fit, xvar = "dev")
```

@@

plot(bootrcvcc, what = "selected", cex = 0.5)
plot(bootrcvcc$fit$glmnet.fit, xvar = "norm")
plot(bootrcvcc$fit$glmnet.fit, xvar = "lambda")
plot(bootrcvcc$fit$glmnet.fit, xvar = "dev")
```

>>>>

plot(bootrcv, what = "selected", cex = 0.5)
plot(bootrcv$fit, what = "path", xvar = "norm", nlabel = 14, cex.lab = 0.5)
plot(bootrcv$fit, what = "path", xvar = "lambda", nlabel = 14, cex.lab = 0.5)
plot(bootrcv$fit, what = "path", xvar = "dev", nlabel = 14, cex.lab = 0.5)
```

@@

plot(bootrcvcc, what = "selected", cex = 0.5)
plot(bootrcvcc$fit, what = "path", xvar = "norm", nlabel = 14, cex.lab = 0.5)
plot(bootrcvcc$fit, what = "path", xvar = "lambda", nlabel = 14, cex.lab = 0.5)
plot(bootrcvcc$fit, what = "path", xvar = "dev", nlabel = 14, cex.lab = 0.5)
```
